Twists of supersymmetric gauge theories

### 2020-01-13 paper.tex
2d

\newcommand{\BV}{\mathrm{BV}}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}
\newcommand{\gauge}{\mathrm{gauge}}
\newcommand{\matter}{\mathrm{matter}}
\newcommand{\MU}{\mathrm{MU}}
\renewcommand{\Re}{\mathrm{Re}}
\newcommand{\U}{\mathrm{U}}

\newcommand{\ham}{/\!\!/}

@@

\usepackage{pdflscape}
\usetikzlibrary{shapes.geometric, arrows, positioning, matrix}

\tikzstyle{s16} = [rectangle, rounded corners, text centered, innersep=0pt, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8} = [rectangle, rounded corners, text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\begin{abstract}

\end{abstract}

@@

\begin{table}[htbp]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
 &&&$\bun_G(\CC^5)$ &\\ \hline
 \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{Rank 1} & Mixed Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
 &&&$\bun_G(\CC^4 \times \RR_{\mr{dR}})$ &\\ \hline
 \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{Rank $(1,0)$ Pure} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
 &&& $T^*[-1]\bun_G(\CC^4, BG)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
 &&& $\bun_G(\CC^3 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $(1,0)$ Impure} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
 &&& $\bun_G(\CC^4, BG)_\mr{dR}$ & \\ \hline
  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{Rank $1$ Pure} & Mixed BF Theory & \multirow{2}*{4 (minimal)} \\
 &&& $T^*[-1]\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
 &&& $\bun_G(\CC^2 \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $1$ Impure} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
 &&& $\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)_\mr{dR}$ & \\ \hline
 \multirow{8}*{6} & \multirow{8}*{$(1,1)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{3 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
 &&& $T^*[-1]\bun_G(\CC^2 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,2)$} & {Mixed Chern-Simons Theory} & \multirow{2}*{5} \\
 &&& $\bun_G(\CC \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$ generic} & {Perturbatively trivial (6d Hitchin system)} & \multirow{2}*{6 (topological)} \\
 &&& $\bun_G(\CC^2 \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
 \multirow{8}*{5} & \multirow{8}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{3 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
 &&& $T^*[-1]\bun_G(\CC \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $4$} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
 &&& $\bun_G(\RR^5_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ generic} & {Perturbatively trivial (Haydys-Witten)} & \multirow{2}*{5 (topological)} \\
 &&& $\bun_G(\CC \times \RR^3_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
 \multirow{12}*{4} & \multirow{12}*{$4$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\higgs_G(\CC^2)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & Mixed BF Theory & \multirow{2}*{3} \\
 &&& $T^*[-1]\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,2)$ special} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
 &&& $T^*[-1]\flat_G(\RR^4)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,1)$} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
 &&& $\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
 &&& $\higgs_G(\CC^2)_{\mr{dR}}$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $(2,2)$ generic} & {Perturbatively trivial (Generic Kapustin-Witten)} & \multirow{2}*{4 (topological)} \\
 &&& $\flat_G(\RR^4)_{\mr{dR}}$ & \\ \hline
  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (B)} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, T^*[2](\gg/\gg))$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $2$ (generic)} & {Perturbatively trivial (generic)} & \multirow{2}*{3 (topological)} \\
 &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
 %\multirow{6}*{2} & \multirow{6}*{$(8,8)$} & \multirow{2}*{Rank $(1,0)$} & {} & \multirow{2}*{1 (holomorphic)} \\
 %&&& {} & \\ \cline{3-5}
 %&& \multirow{2}*{Rank $(1,1)$ (B)} & {} & \multirow{2}*{2 (topological)} \\
 %&&& {} & \\ \cline{3-5}
 %&& \multirow{2}*{Rank $(1,1)$ (A)} & {} & \multirow{2}*{2 (topological)} \\
 %&&& {} & \\ \hline
 \end{tabular}
 \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with gauge group $G$ (16 supercharges).}
 \label{table_of_twists_16}
\end{table}

\begin{table}[!h]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
 &&& $\mr{Map}(\CC^3, U /\!/G)$ & \\ \hline
 \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
 &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U /\!/G)$ & \\ \hline
 \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, U /\!/G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
 &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
 &&& $\mr{Map}(\CC^2, U /\!/G)_{\mr{dR}}$ & \\ \hline
 \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)$  & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\RR^3_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
 \label{table_of_twists_16}
\end{table}

\begin{table}[htbp]
 \centering
 \begin{tabular}{c|>{\centering}m{5ex}|c|>{\centering}m{65ex}|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{Rank $(1,0)$} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, R/G)$ & \\ \hline
 \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
 &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/G)$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a chiral multiplet valued in representation $R$ (4 supercharges).}
 \label{table_of_twists_16}
\end{table}

\begin{figure}[hbp]
\begin{tikzpicture}
  \matrix (mat) [nodes in empty cells, minimum width=3.5ex, minimum height=3.5ex, column sep=1.8ex,row sep=6ex]{
   \node (corner) {}; & \node (d10) {10}; & \node (d9) {9}; & \node (d8) {8}; & \node (d7) {7}; & \node (d6) {6}; & \node {$\qquad \quad \ 5$}; && \node (d5) {};& \node {$\qquad \ 4$}; && \node (d4) {}; & &\node (d3) {3}; & \node (d2) {}; &  \\
  \node {8}; &    &   & \node[s16] (88) {$(1,0)_i$};  &   &   &   &&   &&&&   &&&   \\
  \node {7}; &    &   &   & \node[s16] (77) {$1_i$};  &   &   &&   &&&&   &&&   \\
  \node {6}; &    &   &   &   & \node[s16] (66) {$(1,1)_g$};  &   &&   &&&&   &&&   \\
  \node {5}; & \node[s16] (105) {$(1,0)$};  & \node[s16] (95) {$1$};  & \node[s16] (85) {$(1,1)$};  & \node[s16] (75) {$2$}; & \node[s16]  (65){$(2,2)$};  & \node[s16] (55B) {$4$}; & \node[s16] (55A) {$2_g$};  &   &&&&   &&&   \\
  \node {4}; &    &   & \node[s16] (84) {$(1,0)_p$};  & \node[s16] (74) {$1_p$};  & \node[s16] (64) {$(1,1)_s$};  & \node[s16] (54) {$2_s$};  && \node[s16] (44B) {$(2,2)_s$}; & \node[s16] (44K) {$(2,1)$}; & \node[s8] (44A) {$(2,0)$}; & \node[s16] (44g) {$(2,2)_g$};  &   &&&   \\
  \node {3}; &    &   &   &   & \node[s8] (63) {$(1,0)$};  & \node[s8] (53) {$1$};  && \node[s8] (43) {$(1,1)$};  &&&& \node[s8] (33B) {$2_B$}; & \node[s8] (33A) {$2_A$}; &\node[s16] (33g) {$2_g$};  &   \\
  \node {2}; &    &   &   &   &   &   && \node[s4](42) {$(1,0)$};  &&&& \node[s4] (32) {$1$};  &&   \\
  \node (i1) {1}; &   &  &  &  &  &   & &   &&& &   && &   \\};

  \draw[thick] (corner.south west) -- (d2.south west);
  \draw[thick] (corner.north east) -- (i1.south east);

  \draw[dotted] (0.4,-7) -- (0.4,7);
  \draw[dotted] (6.35,-7) -- (6.35,7);
  \draw[dotted] (-2,-7) -- (-2,7);
  \draw[dotted] (-3.8,-7) -- (-3.8,7);
  \draw[dotted] (-4.75,-7) -- (-4.75,7);
  \draw[dotted] (-6.25,-7) -- (-6.25,7);
  \draw[dotted] (-7.1,-7) -- (-7.1,7);

  \draw[arrow] (105) -- (95);
  \draw[arrow] (95) -- (85);
  \draw[arrow] (88) -- (77);
  \draw[arrow] (95) -- (84);
  \draw[arrow] (85) -- (75);
  \draw[arrow] (85) -- (74);
  \draw[arrow] (84) -- (74);
  \draw[arrow] (77) -- (66);
  \draw[arrow] (75) -- (65);
  \draw[arrow] (75) -- (64);
  \draw[arrow] (74) -- (64);
  \draw[arrow] (74) -- (63);
  \draw[arrow] (66) -- (55A);
  \draw[arrow] (65) -- (55B);
  \draw[arrow] (65) -- (54);
  \draw[arrow] (64) -- (54);
  \draw[arrow] (64) -- (53);
  \draw[arrow] (63) -- (53);
  \draw[arrow] (55A) -- (44g);
  \draw[arrow] (55B) -- (44B);
  \draw[arrow] (54) -- (44B);
  \draw[arrow] (54) -- (43);
  \draw[arrow] (53) -- (43);
  \draw[arrow] (53) -- (42);
  \draw[arrow] (44B) -- (33B);
  \draw[arrow] (44A) -- (33A);
  \draw[arrow] (44K) -- (33A);
  \draw[arrow] (44g) -- (33g);
  \draw[arrow] (43) -- (33B);
  \draw[arrow] (43) -- (32);
  \draw[arrow] (42) -- (32);

\end{tikzpicture}
\caption{Orbits of square-zero supercharges.}
\label{fig:superchargeorbits}
\end{figure}

% \begin{figure}
% \begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
% \node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
% \node (91) [s16, below=of 101] {Rank $1$ $d=5$};
% \node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
% \node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
% \node (825) [right=of 82] {};
% \node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
% \node (71) [s16, below=of 81] {Rank $1$ $d=4$};
% \node (72) [s16, below=of 82] {Rank $2$ $d=5$};
% \node (73) [s16, below=of 83] {Rank $1$ $d=7$};
% \node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
% \node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
% \node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
% \node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
% \node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
% \node (51) [s8, below=of 61] {Rank $1$ $d=3$};
% \node (52) [s16, below=of 62] {Rank $2$ $d=4$};
% \node (53) [s16, below=of 63] {Rank $4$ $d=5$};
% \node (54) [s16, below=of 64] {Rank $2$ $d=5$};
% \node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
% \node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
% \node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
% \node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
% \node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
% \node (31) [s4, below=of 41] {Rank $1$ $d=2$};
% \node (32) [s8, below=of 42] {Rank $2$ $d=3$};
% \node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
% \node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
% 
% \draw[arrow] (101) -- (91);
% \draw[arrow] (91) -- (81);
% \draw[arrow] (91) -- (82);
% \draw[arrow] (81) -- (71);
% \draw[arrow] (82) -- (71);
% \draw[arrow] (82) -- (72);
% \draw[arrow] (83) -- (73);
% \draw[arrow] (71) -- (61);
% \draw[arrow] (71) -- (62);
% \draw[arrow] (72) -- (62);
% \draw[arrow] (72) -- (63);
% \draw[arrow] (73) -- (65);
% \draw[arrow] (61) -- (51);
% \draw[arrow] (62) -- (51);
% \draw[arrow] (62) -- (52);
% \draw[arrow] (63) -- (53);
% \draw[arrow] (64) -- (52);
% \draw[arrow] (64) -- (54);
% \draw[arrow] (65) -- (54);
% \draw[arrow] (51) -- (41);
% \draw[arrow] (51) -- (42);
% \draw[arrow] (52) -- (42);
% \draw[arrow] (52) -- (43);
% \draw[arrow] (53) -- (43);
% \draw[arrow] (54) -- (43);
% \draw[arrow] (54) -- (44);
% \draw[arrow] (54) -- (45);
% \draw[arrow] (41) -- (31);
% \draw[arrow] (42) -- (31);
% \draw[arrow] (42) -- (32);
% \draw[arrow] (43) -- (32);
% \draw[arrow] (44) -- (32);
% \draw[arrow] (45) -- (32);
% \draw[arrow] (31) -- (21);
% \draw[arrow] (31) -- (22);
% \draw[arrow] (32) -- (22);
% 
% \node (2d) [dimension, left=of 21] {2d};
% \node (3d) [dimension, above=of 2d] {3d};
% \node (4d) [dimension, above=of 3d] {4d};
% \node (5d) [dimension, above=of 4d] {5d};
% \node (6d) [dimension, above=of 5d] {6d};
% \node (7d) [dimension, above=of 6d] {7d};
% \node (8d) [dimension, above=of 7d] {8d};
% \node (9d) [dimension, above=of 8d] {9d};
% \node (10d) [dimension, above=of 9d] {10d};
% \end{tikzpicture}
% \caption{Orbits of square-zero supercharges.}
% \label{fig:superchargeorbits}
% \end{figure}

@@

In this section we will set up the homological formalism in which we study classical field theory: the BV-BRST formalism.  Most of the material in this section is not original.  We refer the reader to \chris{refs} for more details.  We will conclude the section by describing a number of fundamental examples of classical field theories that are highly structured: partially holomorphic or topological theories.  We will also discuss the concept of \emph{dimensional reduction} of a classical field theory on $M$ along a fibration $M \to N$.  We will use the idea of dimensional reduction to construct many of the supersymmetric field theories which we will consider in the next section.

\subsection{Conventions}
Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2$-grading. \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.  For an element $x$ we denote by $|x|\in\ZZ/2$ the total degree.

Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of symmetric functions on $\cE$ (respectively $\cE_c)$. 
We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted symbolically by an expression of the form
\[\int_M f (\phi, \phi', \dots),\]
where $f$ is a density on $M$ depending on infinite jets of sections of $E$. Note, however, that the integral here is a formal symbol. 
The space of local functionals can be viewed as a subspace
\[
\oloc(\cE) \subset \cO(\cE_c)
\]
where the integral symbol makes sense in earnest when applied to sections which are compactly supported.
We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.

@@

The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.  In brief \chris{...}

\begin{definition}
A \defterm{free BV theory} on a manifold $M$ is the data of:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q_{\mr{BV}} \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to \Dens_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{definition}

We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
\[
\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
\]
This bracket is of cohomological degree $+1$. 
We will now explain how to define the BV bracket.  First note that there is a linear map
\[
\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
\]
defined as follows. 
A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
\[
D_1(-) \cdots D_n(-) \Omega
\]
where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
Without loss of generality, suppose $F$ is of this form. 
Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
\[
\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
\]
where $\phi$ denotes a compactly supported section. 
Define the symmetric multilinear map
\[
\begin{array}{ccccl}
\d_{dR} F & : & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
\end{array}
\]
Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{dR} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
This implies that $\d_{dR} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.

The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
\[
\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
\]
We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{dR}F$:
\[
X_F := \omega \circ \d_{dR} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
\]
This is the Hamiltonian vector field corresponding to $F$. 
Finally, the BV bracket between local functionals $F, G$ is defined by
\[
\{F, G\} = X_F (G) .
\]

@@

Now, we will include interactions in the BV picture.

@@

In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely a pair $Q_{\mr{BV}}, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ that is at least quadratic and satisfies the classical master equation.
The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.

Because of this, we will sometimes refer to the triple $(E, S, \omega)$ instead $(E, Q_{\mr{BV}}, I, \omega)$ as the data of a classical field theory.

@@

\subsection{Composition algebras and minimal supersymmetry}
\label{sect:compositionalgebras}

>>>>

\newcommand{\BV}{\mathrm{BV}}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}
\newcommand{\gauge}{\mathrm{gauge}}
\newcommand{\matter}{\mathrm{matter}}
\renewcommand{\Re}{\mathrm{Re}}
%\newcommand{\U}{\mathrm{U}}

@@

\usepackage{pdflscape}
\usetikzlibrary{shapes.geometric, arrows, positioning}

\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

@@

@@

Throughout the paper we will mostly work with a $\ZZ\times\ZZ/2$-grading. \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading. For an element $x$ we denote by $|x|\in\ZZ/2$ the total degree.

Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of functions on $\cE$ (respectively $\cE_c)$. 
We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted by
\[\int_M f (\phi, \phi', \dots),\]
where $f$ is a density on $M$ depending on infinite jets of sections of $E$. Note, however, that the integral here is a formal symbol. 
The space of local functionals can be viewed as a subspace
\[
\oloc(\cE) \subset \cO(\cE_c)
\]
where we the integral symbol makes sense in earnest on sections which are compactly supported.
We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.

@@

\begin{definition}
A \defterm{free BV theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q_{\mr{BV}} \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to \Dens_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{definition}

We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
\[
\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
\]
This bracket is of cohomological degree $+1$. 
To define the bracket, first note that there is a linear map
\[
\d_{dR} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
\]
defined as follows. 
A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
\[
D_1(-) \cdots D_n(-) \Omega
\]
where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
Without loss of generality, suppose $F$ is of this form. 
Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
\[
\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
\]
where $\phi$ denotes a compactly supported section. 
Define the symmetric multilinear map
\[
\begin{array}{ccccl}
\d_{dR} F & : & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
\end{array}
\]
Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{dR} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
This implies that $\d_{dR} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.

The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega : E \cong E^! [-1]$ and hence an isomorphism of local functions
\[
\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
\]
We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{dR}F$:
\[
X_F := \omega \circ \d_{dR} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
\]
This is the Hamiltonian vector field corresponding to $F$. 
Finally, the BV bracket between local functionals $F, G$ is defined by
\[
\{F, G\} = X_F (G) .
\]

@@

@@

In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely $Q, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ satisfying the classical master equation.
The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.

Because of this, we will sometimes refer to $(E, S, \omega)$ as the data of a classical field theory.

@@

\subsection{Division algebras and minimal supersymmetry}
\label{sect:divisionalgebras}
